Supercritical fluid extraction of essential oil from caraway seeds: experiments, modelling, and parameter estimation

### 2023-12-03 SFE_Design_of_Experiment/Notes/template_Scrartcl.tex
03.10

\usepackage{amsmath,amssymb}
\usepackage{graphicx}

@@

\section{Maximum likelihood}
Let $y^s$ be the vector of all experimental results (random vector) to be used to estimate $p$, and $y^m(p)$. The vector of the corresponding quantities computed by the model $\dot{x}=f(t,x,p)$. For a parallel model, the parameters of which are to be estimated from measurements of an output vector $\dot{y}=g(x)$. We shall call any
oplimizer of $j$, i.e. any $\hat{p}$ that corresponds to an optimal value of the cost function $j$, an estimate of $p$ in the sense of $j$.

The vector $\hat{p}_{ml}$ will be a maximum-likelihood estimate if it maximizes the cost function

@@

If $p$ were fixed, $\pi_y(y^s|p)$ would be the probability density of the random vector $y^s$ being generated by a model with parameters $p$. Here, to the contrary, $y^s$ is fixed and corresponds to the observations. Considered as a function of $p$, $\pi_y(y^s|p)$ is then called the likelihood of $y^s$. The maximum-likelihood method looks for the value of the parameter vector $p$ that gives the highest likelihood to the observed data. In practice, it is often easier to look for $\hat{p}_{ml}$ by maximizing the log-likelihood function which yields the same estimate since the logarithm function is monotonically increasing.

@@

where the vector $y^m(t_i. p^*)$ is the output of a deterministic model, $p^*$ is the true value of the parameter vector and $\epsilon_i$ belongs to a sequence of independent random variables with probability density $\pi_{\epsilon}(\epsilon_i)$. Since the $\epsilon_i$ are independent

@@

For the true value of the parameters, it satisfies $e^y(t_i, p^*)=\epsilon_i$. and, since $y^m$ is deterministic, $\pi_{y_i} (y^s(t_i)|p) = \pi_{\epsilon_i} (e^y(t_i)|p)$. The likelihood of the $n_t$ observations can therefore be written as

@@

\begin{equation}
	\pi_y (y^s|p) = \prod_{i=1}^{n_t} \frac{1}{ \sqrt{2\pi\sigma_i^2} } \exp \left( -\frac{1}{2} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_i} \right) \right)
\end{equation}

@@

\begin{equation}
	\ln (\pi_y (y^s|p)) = (\text{term independent of p}) - \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{ij}^2} \right)
\end{equation}

@@

\begin{equation}
	\frac{\partial}{\partial p} \ln (\pi_y (y^s|p)) =  \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{ij}^2} \frac{\partial y^m(t_i, p)}{\partial p} \right)
\end{equation}

@@

The Fisher information is a way of measuring the amount of information that an observable random variable carries about an unknown parameter of a distribution that models the random variable. The Fisher information matrix is used to calculate the covariance matrices associated with maximum-likelihood estimates.

The Fisher information matrix can be calculated as

\begin{align}
	F(p) &= \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial \ln (\pi_y (y^s|p))}{\partial p} \frac{\partial \ln (\pi_y (y^s|p))}{\partial p}^T \right] \\
	&= \mathop{\mathbb{E}}_{y^s|p} \left[ \sum_{k=1}^{n_t} \left( \frac{y(t_k) - y^m(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y^m(t_k, p)}{\partial p} \right) \times  \sum_{i=1}^{n_t} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p^T} \right) \right]
\end{align}

@@

@@

In other words, the precision to which we can estimate $p$ is fundamentally limited by the Fisher information of the likelihood function.

\section{Experiment design}

The experimental procedure for the collection of the numerical data to be used to estimate the parameters of a given model depends on qualitative choices made at various steps of the modelling. In particular, the tools presented in the previous chapters allow one to choose:

\begin{itemize}
	\item a set of model structures to be considered
	\item location of sensors and actuators to guarantee identifiability (and distinguishably if several rival structures exist)
	\item an estimator and a characterization of parameter uncertainly
\end{itemize}

Once these choices have been made, the experimenter still has some freedom to specify the quantitative experimental conditions (such as temperature, pressure, sampling times, shape of inputs, etc.). Experiment design aims at determining experimental conditions adapted to the final purpose of the modelling. It is a crucial step, for a badly designed experiment may ruin any attempt at analysing the data collected from the system.

Assume that the i'th scalar observation can be written as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ (the i'th support point) describes the experimental conditions (e.g., measurement time, shape of input...) under which the i'th observation is to be collected. When $n_t$ such observations are taken, the concatenation of the vectors $\xi_i$'s yields the $\Xi = (\xi_1, \xi_2,..., \xi_{n_t})$, which characterizes all experimental conditions to be optimized. To make experiment design realistic, it is necessary to take a number of constraints into account, e.g. on the duration of the experiments, the energy or amplitude of the inputs, the minimum time between samples. Let $\bar{\Xi}$ be the set of all feasible values for $\Xi$.

The definition of a cost function $j$ then permits optimal experiment design to be cast as a constrained optimization problem, where the optimal experiment $\Xi^*$ is defined by

@@

Evaluation of the cost function $j$ must be simple enough to allow easy optimization. For that reason, classical oplimality criteria correspond to a scalar function of the Fisher information matrix $F(p,\Xi)$

@@

Under the hypotheses mentioned above, the distribution of the maximum likelihood estimator is asymptotically Gaussian $\mathop{\mathbb{N}} (p^*, F^{-1}([^*, \Xi])) $ when the number of measurements tends to infinity. Minimizing $j(\Xi)$ then amounts to minimizing a scalar easure of the asymptotic covariance matrix of the parameters.

A rather general class of optimality criteria employs the following family of cost functions

@@

A D-optimal experiment minimizes the volume of the asymptotic confidence ellipsoids for the parameters.

\begin{figure}[h]
	\centering
	\includegraphics[width=8cm]{DOE_conditions.jpg}
\end{figure}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{tikz}

@@

\section{Maximum likelihood}
Let $y^s$ be the vector of all experimental results (random vector) to be used to estimate $p$ and $y^m(p)$. The vector of the corresponding quantities computed by the model $\dot{x}=f(t,x,p)$. For a parallel model, the parameters of which are to be estimated from measurements of an output vector $\dot{y}=g(x)$. We shall call any optimizer of $j$, i.e., any $\hat{p}$ that corresponds to an optimal value of the cost function $j$, an estimate of $p$ in the sense of $j$.

The vector $\hat{p}_{ml}$ will be a maximum-likelihood estimate if it maximizes the cost function:

@@

If $p$ were fixed, $\pi_y(y^s|p)$ would be the probability density of the random vector $y^s$ generated by a model with parameters $p$. Here, to the contrary, $y^s$ is fixed and corresponds to the observations. Considered as a function of $p$, $\pi_y(y^s|p)$ is then called the likelihood of $y^s$. The maximum-likelihood method looks for the parameter vector $p$ value that gives the observed data the highest likelihood. In practice, it is often easier to look for $\hat{p}_{ml}$ by maximizing the log-likelihood function, yielding the same estimate since the logarithm function is monotonically increasing.

@@

where the vector $y^m(t_i. p^*)$ is the output of a deterministic model, $p^*$ is the true value of the parameter vector, and $\epsilon_i$ belongs to a sequence of independent random variables with probability density $\pi_{\epsilon}(\epsilon_i)$. Since the $\epsilon_i$ are independent

@@

For the true value of the parameters, it satisfies $e^y(t_i, p^*)=\epsilon_i$. and, since $y^m$ is deterministic, $\pi_{y_i} (y^s(t_i)|p) = \pi_{\epsilon_i} (e^y(t_i)|p)$. The likelihood of the $n_t$ observations can be written as

@@

\begin{equation}
	\pi_y (y^s|p) = \prod_{i=1}^{n_t} \frac{1}{ \sqrt{2\pi\sigma_{t_i}^2} } \exp \left( -\frac{1}{2} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}} \right) \right)
\end{equation}

@@

\begin{equation}
	\ln (\pi_y (y^s|p)) = (\text{term independent of p}) - \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \right)
\end{equation}

@@

\begin{equation}
	\frac{\partial}{\partial p} \ln (\pi_y (y^s|p)) =  \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p} \right)
\end{equation}

@@

The Fisher information is a way of measuring the amount of information that an observable random variable carries about an unknown parameter of a distribution that models the random variable. The Fisher information is related to the second derivative (or the curvature) of the log-likelihood function with respect to the parameter. This relationship provides a measure of how "sensitive" the likelihood is to changes in the parameter value. The Fisher information matrix can be calculated as follow.

\begin{align}
	F(p) &= - \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial^2 \ln (\pi_y (y^s|p))}{\partial p \partial p^T} \right] = \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial \ln (\pi_y (y^s|p))}{\partial p} \frac{\partial \ln (\pi_y (y^s|p))}{\partial p^T} \right] \\
	&= \mathop{\mathbb{E}}_{y^s|p} \left[ \sum_{k=1}^{n_t} \left( \frac{y(t_k) - y^m(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y^m(t_k, p)}{\partial p} \right) \times  \sum_{i=1}^{n_t} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p^T} \right) \right]
\end{align}

@@

If every experiment at time $t_i$ is independent and characterized by its own $\sigma_{t_i}$, then the Fisher information matrix can be presented in the more compact way:

\begin{equation}
	F(p) = \frac{\partial y^m(t, p)}{\partial p} \text{diag}\left(\frac{1}{\sigma_{t}^2}\right) \frac{\partial y^m(t, p)}{\partial p^T} 
\end{equation}

@@

In other words, the precision to which we can estimate $p$ is fundamentally limited by the Fisher information of the likelihood function. Based on the Cramer-Rao inequality, the Fisher information matrix can used to calculate the covariance matrices associated with maximum-likelihood estimates.

\section{Optimal experimental design}

The optimal design of experiments (DOE) is a statistical concept that refers to the process of planning an experiment, which allow parameters to be estimated without bias and with minimum variance. Optimal design ensures that the experiment can provide the most informative data possible. This often involves balancing the study of main effects and interactions between factors. Moreover, by efficiently planning experiments, optimal design aims to reduce the overall resources required, such as time, materials, and manpower.

The methodology for data to estimate the parameters of a specific model is influenced by a series of qualitative decisions made throughout the experimental and modelling process, such as: a model structure, a location of sensors or an equipment. Once these choices have been made, the experimenter still has some freedom to specify the quantitative experimental conditions (such as temperature, pressure, sampling times, etc.). Experiment design aims to determine experimental conditions adapted to the final purpose of the modeling.

%Assume that the i'th scalar observation can be written as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ (the i'th support point) describes the experimental conditions (e.g., measurement time, the shape of input, etc.) under which the i'th observation is to be collected. When $n_t$ such observations are taken, the concatenation of the vectors $\xi_i$'s yields the $\Xi = (\xi_1, \xi_2,..., \xi_{n_t})$, which characterizes all experimental conditions to be optimized. To make the experiment design realistic, it is necessary to consider several constraints, e.g., the experiments' duration, the inlet stream's temperature, and the minimum time between samples. Let $\bar{\Xi}$ be the set of all feasible values for $\Xi$.

Let's consider that each scalar observation in our study can be expressed as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ representing the specific experimental conditions (such as the timing of measurements, operating conditions, etc.) under which the i'th observation is gathered. When collecting $n_t$ such observations, the assembly of these $\xi_i$ vectors forms the matrix $\Xi = (\xi_1, \xi_2,..., \xi_{n_t})$, which combine all the experimental conditions that need optimization. In order to align the design of the experiment with practical realities, it's important to take into account various constraints, such as the total duration of the experiments, the maximum temperature of the inlet stream, and the minimum interval between sampling events. The set of all possible combinations for $\bar{\Xi}$ that adhere to these constraints is denoted as $\Xi$.

%The definition of a cost function $j$ then permits the optimal experiment design to be cast as a constrained optimization problem, where the optimal experiment $\Xi^*$ is defined by

The formulation of a cost function $j$ allows for the framing of optimal experiment design as a problem of constrained optimization. In this context, the optimal experiment, denoted as $\Xi^*$:

@@

The cost function should describe the amount of information from an experiment. For that purpose it can be assumed a function $\phi$ can be related to the Fisher information obtained an arbitrary operating conditions.

@@

%Under the hypotheses mentioned above, the distribution of the maximum likelihood estimator is asymptotically Gaussian $\mathop{\mathbb{N}} (p^*, F^{-1}([^*, \Xi])) $ when the number of measurements tends to infinity. Minimizing $j(\Xi)$ then amounts to minimizing a scalar measure of the asymptotic covariance matrix of the parameters.

A general class of optimality criteria for DOE is given by

@@

A D-optimal experiment minimizes the volume of the asymptotic confidence ellipsoids for the parameters. The graphical representation of the different optimality conditions is shown in Figure \ref{fig:score_fun}.

\begin{figure}[!h]
	\centering
	\resizebox{0.4\textwidth}{!}{%
	\begin{tikzpicture}
		% Ellipse parameters
		\def\ellipsecenter{(3,3)}
		\def\ellipseA{(0.75,5.25)} % End point for A-optimality arrow
		\def\ellipseB{(5.13,5.13)} % End point for E-optimality arrow
		\def\ellipseC{(4,1.2)}      % End point for D-optimality arrow

		% Draw the rotated ellipse
		\draw[fill=gray!10, draw=black, rotate around={45:\ellipsecenter}] \ellipsecenter ellipse (3cm and 1cm);

		% Draw the dashed rectangle
		\draw[dashed] (0.75,0.75) rectangle (5.25,5.25);

		% Draw the arrows and label them with adjustable positions
		\draw [-latex] \ellipsecenter -- \ellipseA node[yshift=-4cm, xshift=2.5cm,rotate around={-45:\ellipsecenter}] {A-optimality};
		\draw [-latex] \ellipsecenter -- \ellipseB node[yshift=0cm, xshift=-3.9cm,rotate around={45:\ellipsecenter}] {E-optimality};
		\draw [-latex] \ellipseC -- (2,2) node[yshift=-1cm, xshift=2cm] {D-optimality};

		% Draw axes
		\draw[thick,->] (0,0) -- (6,0) node[below] {$p_1$};
		\draw[thick,->] (0,0) -- (0,6) node[left] {$p_2$};
	\end{tikzpicture}
	}%
	\caption{Graphical representation of score functions}
	\label{fig:score_fun}
\end{figure}

### 2023-12-03 SFE_article_Parameter_Estimation/Sections/Experiments.tex
03.10

	%The results of experiments are presented in the Table \ref{tab: Yield_data}.

%	\begin{table}[!h]
%		\centering
%		\adjustbox{max width=\columnwidth}{%
%			\csvautobooktabular{Figures/Results_estimation/Dataset.csv} }
%		\caption{Yield data; cumulative amount of solute [g] collected every 5 min}
%		\label{tab: Yield_data}
%	\end{table}

>>>>

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
			\caption{Experiment at $40~^\circ C$ and 200 bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
			\caption{Experiment at $50~^\circ C$ and 200 bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300.pdf}
			\caption{Experiment at $40~^\circ C$ and 300 bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300.pdf}
			\caption{Experiment at $50~^\circ C$ and 300 bar}
		\end{subfigure}
		\caption{Results of parameter estimation}
		\label{fig: estimation_results}
	\end{figure}

### 2023-12-03 SFE_article_Parameter_Estimation/Supercritical_fluid_extraction_of_essential_oil_from_caraway.tex
03.10

%\author[1]{Francesco Corona}[orcid=0000-0002-3615-1359]
%\credit{c}

@@

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
%Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ is the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output. As an example, the supercritical extraction process is presented. The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed. The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems. Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
%Given a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ represents state variables, $\Theta$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process. The process model describes a partially filled extractor with a fixed bed, which work under constant operating conditions. We assume that the flow is uniform across any cross-section, although the area available for the fluid phase can change along the extractor. We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
%In this work, a distributed-parameter model, based on \citet{Reverchon1996} is used to describe a fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent. The model parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient \textit{and saturation concentration} are obtained from parameter estimation. The parameters are estimated based on four experiments performed at $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar and $50^\circ C$/$300$ bar. Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
This study aimed to investigate the supercritical extraction process of the caraway oil from caraway seeds. A distributed-parameter model is used to describe the fluid-solid extraction process with carbon dioxide as a solvent. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated from the Peng-Robinson equation of state. This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient. The missing model parameters and the initial state are obtained by solving the maximum likelihood estimation based on experimental yield data under the normal error assumption. A set of laboratory experiments was performed in a partially filled extractor with a fixed bed operated under multiple constant operating conditions: $40~^\circ C$ / $200$ bar, $50~^\circ C$ / $200$ bar, $40~^\circ C$ / $300$ bar, and $50~^\circ C$ / $300$ bar.

@@

\section{Introduction}
%\subfile{Sections/introduction}
\subfile{Sections/introduction_imp}

@@

\subsection{Supercritical fluids} \label{CH: Thermodynamic}
%\subfile{Sections/Thermo}
\subfile{Sections/Thermo_imp}

%\clearpage
%\subfile{Sections/Materials_and_methods}

\subsection{Governing equations} \label{CH:Governing_equations_chapter}
%\footnote{For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
%	{\color{red}control variables},
%	{\color{black}state variables},
%	{\color{black}variables} and
%	{\color{black}parameters}.} 
	The governing equation for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the Appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}. Quasi-one-dimensional flow is a fluid flow characterized by the assumption that the flow properties remain uniform across any given cross-section of the flow. This assumption is made when there is a variation in the cross-sectional area of the flow channel, such as an irregular shape or partial filling of an extractor. In such cases, the flow is considered to be quasi-one-dimensional because the velocity and other flow properties are assumed to vary only in the direction of flow.

@@

Suppose the flow is presumed to be isentropic, $d{\color{black}P}/d{\color{black}\rho_f} = c^2$, so $v^2=c^2$, where $c$ is the speed of sound. This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow. Moreover, if the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic which leads to $\partial {\color{black}\rho_f} / \partial {\color{black}P} \approx 0$. In other words, the small changes in pressure due to flow velocity changes do not change the density. %This has a secondary effect -- the speed of sound in the fluid is $\partial {\color{black}P}/\partial {\color{black}\rho_f} = \infty$ in this instance. So there is an infinite speed of sound, which makes the equations elliptic in nature. It can be deduced that at the isothermal conditions, the density in the system propagates with the same speed as pressure since they are both connected through the equation of state. The details of the Mach-number analysis are presented in Appendix \ref{CH:Low_Mach_chapter}.

@@

%\newpage
%\section{Bayes theorem} \label{CH: Bayes}
%\subfile{Sections/Bayes_Theorem}
%\clearpage

@@

\clearpage \appendix \label{appendix}
\section{Appendix} 
\subsection{Thermodynamic}
\subfile{Sections/Qubic_EOS}
%\subfile{Sections/Thermodynamic_details}

@@

%\subsection{Low Mach number expansion} \label{CH:Low_Mach_chapter}
%\subfile{Sections/Low_mach_number_expansion}
%\subfile{Sections/Low_mach_number_expansion_imp}

@@

%\subsection{Bayes theorem} \label{CH: Bayes}
%\subfile{Sections/Bayes_Theorem}

@@

%\subsection{Concentration profiles} \label{CH: Profiles}
%\subfile{Sections/Profiles}

%\subsection{Solution of the parameter estimation starting from another initial guess} \label{CH: Profiles_2}
%\subfile{Sections/Parameter_estimation_solution_from_another_IG}

>>>>

@@

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study investigated the supercritical extraction process of caraway oil from caraway seeds. A distributed-parameter model describes the fluid-solid extraction process. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated from the Peng-Robinson equation of state. Key model parameters included partition factor internal and axial diffusion coefficients. These parameters and the initial state were determined using maximum likelihood estimation from experimental data, assuming normal error. A set of laboratory experiments was performed in a partially filled extractor with a fixed bed operated under multiple constant operating conditions: $40~^\circ C$ / $200$ bar, $50~^\circ C$ / $200$ bar, $40~^\circ C$ / $300$ bar, and $50~^\circ C$ / $300$ bar.

@@

\section{Introduction}
\subfile{Sections/introduction_imp}

@@

\subsection{Supercritical fluids} \label{CH: Thermodynamic}
\subfile{Sections/Thermo_imp}

\subsection{Governing equations} \label{CH:Governing_equations_chapter}
	The governing equation for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the Appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}. Quasi-one-dimensional flow is a fluid flow characterized by the assumption that the flow properties remain uniform across any given cross-section of the flow. This assumption is made when there is a variation in the cross-sectional area of the flow channel, such as an irregular shape or partial filling of an extractor. In such cases, the flow is considered to be quasi-one-dimensional because the velocity and other flow properties are assumed to vary only in the direction of flow.

@@

Suppose the flow is presumed to be isentropic, $d{\color{black}P}/d{\color{black}\rho_f} = c^2$, so $v^2=c^2$, where $c$ is the speed of sound. This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow. Moreover, if the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic which leads to $\partial {\color{black}\rho_f} / \partial {\color{black}P} \approx 0$. In other words, the small changes in pressure due to flow velocity changes do not change the density.

@@

@@

\clearpage \appendix \label{appendix}
\section{Appendix} 
\subsection{Thermodynamic}
\subfile{Sections/Qubic_EOS}

@@

@@

@@
